% CV ----
% This is just here so I know exactly what I'm looking at in Rstudio when messing with stuff.
\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
% \usepackage{titlesec}
% \titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}
% \titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\scriptsize  A. Zeynep Enkavi - CV}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={A. Zeynep Enkavi:  CV (Curriculum Vitae)},
            pdfauthor={A. Zeynep Enkavi},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

% \emph{Updated:} \apstylekinda\today
% ^ removed from that front bar.

\usepackage{orcidlink}
%\usepackage{academicons}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
% \newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}

\begin{document}


\centerline{\huge \bf A. Zeynep Enkavi}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Postdoctoral Scholar, Rangel
Neuroeconomics Lab}
\moveleft.5\hoffset\centerline{Caltech · 1200 E. California Blvd, MC
228-77, Pasadena, CA 91125}
%\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:zenkavi@caltech.edu}{\nolinkurl{zenkavi@caltech.edu}}} \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/zenkavi}{\tt zenkavi} \hspace{1 mm}   \faTwitter \hspace{1 mm} \href{https:/twitter.com/zeynepenkavi}{\tt zeynepenkavi} \hspace{1 mm}   \orcidlink{0000-0001-7040-3620} \hspace{.5 mm} \href{https://orcid.org/0000-0001-7040-3620}{\tt 0000-0001-7040-3620} \hspace{1 mm}  \faGlobe \hspace{1 mm} \href{http://zenkavi.github.io/}{\tt zenkavi.github.io/}    | \emph{Updated:} 11
Jun 2023}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:zenkavi@caltech.edu}{\nolinkurl{zenkavi@caltech.edu}}} \hspace{1 mm} 
 \faGithub \hspace{1 mm} \href{http://github.com/zenkavi}{\tt zenkavi} \hspace{1 mm}   \faTwitter \hspace{1 mm} \href{https:/twitter.com/zeynepenkavi}{\tt zeynepenkavi} \hspace{1 mm}   \orcidlink{0000-0001-7040-3620} \hspace{.5 mm} \href{https://orcid.org/0000-0001-7040-3620}{\tt 0000-0001-7040-3620} \hspace{1 mm}  \faGlobe \hspace{1 mm} \href{http://zenkavi.github.io/}{\tt zenkavi.github.io/}    | \emph{Updated:} 11
Jun 2023}

\vspace{2 mm}

\hrule



\hypertarget{education}{%
\section{Education}\label{education}}

\emph{Stanford University} \hfill 2019\\
Ph.D.~in Psychology (Neuroscience)\\
Adviser: Russell A. Poldrack

\emph{University of Pennsylvania} \hfill 2012\\
B.A. in Cognitive Science, German Studies and Science, Technology and
Society\\
Adviser: Joseph W. Kable

\hypertarget{employment}{%
\section{Employment}\label{employment}}

\emph{California Institute of Technology} \hfill 2019-Present\\
Rangel Neuroeconomics Lab Postdoctoral Scholar\\
Adviser: Antonio Rangel

\emph{Columbia Business School} \hfill 2012-14\\
Center for Decision Sciences Lab Manager\\
Advisers: Eric J. Johnson, Elke U. Weber

\hypertarget{honors-and-awards}{%
\section{Honors and Awards}\label{honors-and-awards}}

Penn World Scholars \hfill 2008-12\\
University of Pennsylvania

Erich Friedmann Memorial Prize \hfill 2012\\
University of Pennsylvania

Daniel B Shumway Prize \hfill 2009\\
University of Pennsylvania

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{in-preparation}{%
\subsection{In preparation}\label{in-preparation}}

\textbf{Enkavi, A. Z.}, Lombardi, G., Hare, T., Rangel, A. Human simple
choice in non-human experiments.

\textbf{Enkavi, A. Z.}, Tavares, G., Rangel, A. Choosing between bundles
of described and experienced risks.

\textbf{Enkavi, A. Z.}, Helfinstein, S., Poldrack, R. A. Statistically
the same but cognitively different models of risky behavior during
adolescence.

\hypertarget{peer-reviewed}{%
\subsection{Peer-reviewed}\label{peer-reviewed}}

\textbf{2022}

Kliemann, D., Armstrong, T., Galdi, P., Kahn, D., Rusch, T.,
\textbf{Enkavi, A. Z.}, Liang, D., Lograsso, S., Zhu, W., Yu, R., Nair,
R., Paul, L., Tyszka, J. M., Adolphs, R. (2022) Caltech Conte Center - A
multimodal data resource for exploring social cognition and
decision-making. \emph{Scientific Data}, 9 (1), 1-15.

\textbf{2021}

\textbf{Enkavi, A. Z.}, Poldrack, R. A. (2021). Implications of the
lacking relationship between cognitive task and self report measures for
psychiatry. \emph{Biological Psychiatry: Cognitive Neuroscience and
Neuroimaging}, 6 (7), 670-672.

Mazza, G. L., Smyth, H. L., Bissett, P. G, Canning, J. R., Eisenberg, I.
W., \textbf{Enkavi, A. Z.}, Gonzalez, O., Kim, S. J., Metcalf, S. A.,
Muniz, F., Pelham III, W. E., Scherer E. A., Valente, M. J., Xie, H.,
Poldrack, R. A., Marsch, L. A., MacKinnon, D. P. (2021). Correlation
Database of 60 Cross-Disciplinary Surveys and Cognitive Tasks Assessing
Self-Regulation. \emph{Journal of Personality Assessment}, 103 (2),
238-245.

\textbf{2019}

\textbf{Enkavi, A. Z.}, Eisenberg, I. W., Bissett, P. G., Mazza, G. L.,
MacKinnon, D. P., Marsch, L. A., \& Poldrack, R. A. (2019). Reply to
Friedman and Banich: Right measures for the research question.
\emph{Proceedings of the National Academy of Sciences}, 116 (49),
24398-24399.

Eisenberg, I. W., Bissett, P. G., \textbf{Enkavi, A. Z.}, Li, J.,
MacKinnon, D. P., Marsch, L. A., \& Poldrack, R. A. (2019). Uncovering
the structure of self-regulation through data-driven ontology discovery.
\emph{Nature communications}, 10 (1), 2319.

\textbf{Enkavi, A. Z.}, Eisenberg, I. W., Bissett, P. G., Mazza, G. L.,
MacKinnon, D. P., Marsch, L. A., \& Poldrack, R. A. (2019). Large-scale
analysis of test--retest reliabilities of self-regulation measures.
\emph{Proceedings of the National Academy of Sciences}, 116 (12),
5472-5477.

\textbf{Pre - 2019}

Eisenberg, I. W., Bissett, P. G., Canning, J. R., Dallery, J.,
\textbf{Enkavi, A. Z.}, Whitfield-Gabrieli, S., \ldots{} \& Kim, S. J.
(2018). Applying novel technologies and methods to inform the ontology
of self-regulation. \emph{Behaviour research and therapy}, 101, 46-57.

\textbf{Enkavi, A. Z.}, Weber, B., Zweyer, I., Wagner, J., Elger, C. E.,
Weber, E. U., \& Johnson, E. J. (2017). Evidence for hippocampal
dependence of value-based decisions. \emph{Scientific reports}, 7 (1),
17738.

Sochat, V. V., Eisenberg, I. W., \textbf{Enkavi, A. Z.}, Li, J.,
Bissett, P. G., \& Poldrack, R. A. (2016). The experiment factory:
standardizing behavioral experiments. \emph{Frontiers in psychology}, 7,
610.

Li, Y., Gao, J., \textbf{Enkavi, A. Z.}, Zaval, L., Weber, E. U., \&
Johnson, E. J. (2015). Sound credit scores and financial decisions
despite cognitive aging. \emph{Proceedings of the National Academy of
Sciences}, 112 (1), 65-69.

\hypertarget{invited-talks}{%
\section{Invited Talks}\label{invited-talks}}

\emph{2022}: NIMH RDoC Roundtable (Virtual)\\
\emph{2021}: Cognitive Sciences Colloquium, UC Irvine (Virtual)\\
\emph{2018}: Cognitive and Neuroscience Seminar Series, Stanford

\hypertarget{conference-presentations}{%
\section{Conference presentations}\label{conference-presentations}}

\hypertarget{talks}{%
\subsection{Talks}\label{talks}}

Enkavi, A. Z. (2023), ``Human simple choice in a non-human primate
paradigm'', Interdisciplinary Symposium on Decision Neuroscience, Temple
University.

Enkavi, A. Z. (2023), ``Human simple choice in a non-human primate
paradigm'', Social and Decision Neuroscience Symposium Series, Caltech.

Enkavi, A. Z. (2015), ``Preference consistency relies on hippocampal
function: Evidence from mediotemporal lobe epilepsy'', Interdisciplinary
Symposium on Decision Neuroscience, MIT.

\hypertarget{posters}{%
\subsection{Posters}\label{posters}}

Enkavi, A. Z., Tavares, G., Rangel, A. ``Choice between multi-attribute
and multi-modal uncertainties'' 2022. Society for Neuroeconomics Annual
Meeting, Arlington, VA.

Enkavi, A. Z., Tavares, G., Rangel, A. ``Choosing between bundles of
described and experienced risks'' 2022. The Neurobiology of Reward And
Decision-Making (II), Lake Arrowhead, California.

Enkavi, A. Z., Eisenberg, I. W., Bissett, P. G., Mazza, G. L, MacKinnon,
D. P., Marsch, L. A., Poldrack, R. A., ``A large scale analysis of
cognitive task measures of self-regulation'' 2018. Society for
Neuroeconomics Annual Meeting, Philadelphia, Pennsylvania.

Enkavi, A. Z., Eisenberg, I. W., Bissett, P. G., Mazza, G. L, MacKinnon,
D. P., Marsch, L. A., Poldrack, R. A., ``A large scale analysis of
test-retest reliabilities of self-regulation measures'' 2017. Society of
Judgment and Decision Making Annual Meeting, Vancouver, Canada.

Enkavi, A. Z., Eisenberg, I. W., Bissett, P. G., Mazza, G. L, MacKinnon,
D. P., Marsch, L. A., Poldrack, R. A., ``A large scale analysis of
test-retest reliabilities of self-regulation measures'' 2017. Society
for Neuroeconomics Annual Meeting, Toronto, Canada.

Enkavi, A. Z., McClure, S. M, ``Beyond Delay Discounting: Intertemporal
Choice Between Non-Unitary Rewards'' 2015. Society of Judgment and
Decision Making Annual Meeting, Chicago, Illinois.

Enkavi, A. Z., McClure, S. M, ``Beyond Delay Discounting: Intertemporal
Choice Between Non-Unitary Rewards'' 2015 Society for Neuroeconomics
Annual Meeting, Miami, Florida.

Enkavi, A. Z., Gao, J., Li, Y., Johnson E. J., Weber, E. U. What
Measures of Risk Attitude Predict Real World Risk Taking? 2014. Society
of Judgment and Decision Making Annual Meeting, Long Beach, California.

Enkavi, A. Z., Weber, B., Zweyer, I., Wagner, J., Elger, C. E., Weber,
E. U., Johnson, E. J. Preference consistency relies on hippocampal
function: Evidence from mediotemporal lobe epilepsy. 2014. Society of
Judgment and Decision Making Annual Meeting, Long Beach, California.

Kazinka, R., Enkavi, A. Z., Vo, K., Kable, J. W. Individual differences
in the Asymmetric Dominance Effect. 2014. Society for Neuroeconomics
Annual Meeting, Miami, Florida.

Enkavi, A. Z., Gao, J., Li, Y., Zaval, L., Johnson E. J., Weber, E. U.
Neurons die, not knowledge: Domain knowledge compensates for declining
cognitive ability in financial decision-making. 2013. Society of
Judgment and Decision Making Annual Meeting, Toronto, Canada.

\hypertarget{training-courses-attended}{%
\section{Training Courses Attended}\label{training-courses-attended}}

Evidence-Based Undergraduate STEM Teaching\hfill 2023\\
First Year Faculty Teaching Academy\hfill 2023\\
Neuromatch Academy\hfill 2020\\
OHBM: Fundamental Concepts and Methods in Network Neuroscience
\hfill 2020\\
OHBM Brainhack hackathon \hfill 2018\\
SRNDNA computational modeling workshop for Decision Neuroscience and
Aging \hfill 2015

\hypertarget{teaching-and-mentorship}{%
\section{Teaching and Mentorship}\label{teaching-and-mentorship}}

Brain and Decision Making, TA \hfill 2018\\
Introduction to Statistical Methods, Coding assistance \hfill 2018\\
Psych One Teaching Fellow \hfill 2015-17\\
Introduction to Learning and Memory, TA \hfill 2016\\
Introduction to Cognitive Neuroscience, TA \hfill 2016

\emph{Research advising}

Vinh Ton, Stanford University \hfill 2016-18\\
Dimitrios Konstantellos, MIT \hfill 2017\\
Brian Wu, University of California, Berkeley \hfill 2016\\
Andrea Bell, Columbia University \hfill 2014\\
Joachim Talloen, Rutgers University \hfill 2014\\
Tae Ho Kim, University of Chicago \hfill 2013

\hypertarget{service}{%
\section{Service}\label{service}}

Caltech Postdoc Association Division co-representative, Caltech
\hfill 2022-Present\\
Graduate student cohort co-representative, Stanford University
\hfill 2014-19\\
Graduate student interview weekend co-organizer, Stanford University
\hfill 2016

\hypertarget{ad-hoc-reviewer}{%
\section{Ad hoc Reviewer}\label{ad-hoc-reviewer}}

Behavior Research Methods, Biological Psychiatry, Cerebral Cortex,
Computational Psychiatry, Journal of Neuroscience, Psychology and
Economics, Nature Human Behaviour, NeuroImage, Neuropsychopharmacology,
Trends in Cognitive Sciences

\hypertarget{references}{%
\section{References}\label{references}}

Antonio Rangel, Ph.D.\\
California Institute of Technology

Russell A. Poldrack, Ph.D.\\
Stanford University

Bridgette Martin-Hard, Ph.D.\\
Duke University

Eric J. Johnson, Ph.D.\\
Columbia Business School

Elke U. Weber, Ph.D.\\
Princeton University

Joseph W. Kable, Ph.D.\\
University of Pennsylvania

\end{document}
